Characterizing the response of subarctic European vegetation to key environmental variables for land surface modeling of ozone pollution and risk assessment

### 2021-10-13 VegOzone.tex
Change running title
Implement suggestions by Lisa

\runningtitle{Subarctic biomes for land surface modeling}

@@

\authorcontribution{SF has written the manuscript, collected and processed ozone and environmental data, and performed all statistical analyses. AVV contributed to framing this research article, has performed the on-site observation of vegetation damage induced by ozone, and advising in plant physiological processes. LE has contributed to framing of the this article, $\mathrm{DO_3SE}$ modeling, and development of the PDF-based temperature acclimation. CO has collected PFT parameters from literature, performed all $\mathrm{DO_3SE}$ simulations and validation of the results. AE contributed with her experience regarding subarctic vegetation in Finnmark. FS contributed with an assessment of the 2018 meteorological conditions. TB gave guidance in a broader research sense. All authors contributed to discussions, writing, and conclusions.} %% this section is mandatory

>>>>

\runningtitle{Response of subarctic European vegetation to key environmental variables}

@@

\authorcontribution{SF has written the manuscript, collected and processed ozone and environmental data, and performed all statistical analyses. AVV contributed to framing this research article, has performed the on-site observation of vegetation damage induced by ozone, and provided advice on plant physiological processes. LE has contributed to framing of the this article, $\mathrm{DO_3SE}$ modeling, and development of the PDF-based temperature acclimation assessment. CO has collected PFT parameters from the literature, performed all $\mathrm{DO_3SE}$ simulations and validation. AE contributed with her experience regarding subarctic vegetation in Finnmark. FS contributed with an assessment of the 2018 meteorological conditions. TB gave guidance in a broader research sense. All authors contributed to discussions, writing, and conclusions.} %% this section is mandatory
